Parental migration, cognitive development and educational performance

### 2022-05-20 data/Gu-thesis-script.Rmd
z-score calculation before sampling; sampling children with 7 years or longer local residency

---
title: "Effect of Parental Absence on Adolescents' Academic Performance"
output: html_notebook
---

@@

```{r}
d <- d %>% mutate(
  age = 2013 - a02a, #children's age at baseline
  local.resi = age - a07 #years of residence at the current county05
)
```

Sample
```{r}
d_cl <- d %>% 
  filter(w2a0801==1) %>% #parents who are married (and alive)
  filter(be1201==1 & be1202==1) %>% #both parents stay with children at baseline
  filter(local.resi>=5)
```

## Variables 
Compute standardized exam grades (within-school z-scores)
```{r}
d_cl <- d_cl %>% #Total exam grades at wave 1 and at wave 2
  mutate(w1ttl = tr_chn + tr_mat + tr_eng, 
         w2ttl = w2chn + w2mat + w2eng) 
d_cl <- d_cl %>% #Within-school z-scores for Chinese, math, English exams and their total, respectively
  group_by(schids) %>%
  mutate(w1chn_std = as.numeric(scale(tr_chn)),
         w1mat_std = as.numeric(scale(tr_mat)),
         w1eng_std = as.numeric(scale(tr_eng)),
         w1ttl_std = as.numeric(scale(w1ttl)),
         w2chn_std = as.numeric(scale(w2chn)),
         w2mat_std = as.numeric(scale(w2mat)),
         w2eng_std = as.numeric(scale(w2eng)),
         w2ttl_std = as.numeric(scale(w2ttl))
         ) %>% ungroup()
```

Dependent variables: Outcome differences between wave 2 and wave 1
```{r}
d_cl <- d_cl %>% mutate(
  chn_std = w2chn_std - w1chn_std,
  mat_std = w2mat_std - w1mat_std,
  eng_std = w2eng_std - w1eng_std,
  ttl_std = w2ttl_std - w1ttl_std,
  cog = w2cog3pl - cog3pl #Cognitive test score, standardized
) %>%
  drop_na(cog, chn_std, mat_std, eng_std, ttl_std)
```

>>>>

---
title: "Parental migration, cognitive development and educational performance"
output: html_notebook
---

@@

```{r}
d <- d %>% mutate(
  age = 2014 - a02a, #children's age at baseline
  local.resi = age - a07 #years of residence at the current county05
)
```

Compute standardized exam grades (within-school z-scores)
```{r}
d <- d %>% #Total exam grades at wave 1 and at wave 2
  mutate(w1ttl = tr_chn + tr_mat + tr_eng, 
         w2ttl = w2chn + w2mat + w2eng) 
d <- d %>% #Within-school z-scores for Chinese, math, English exams and their total, respectively
  group_by(schids) %>%
  mutate(w1chn_std = as.numeric(scale(tr_chn)),
         w1mat_std = as.numeric(scale(tr_mat)),
         w1eng_std = as.numeric(scale(tr_eng)),
         w1ttl_std = as.numeric(scale(w1ttl)),
         w2chn_std = as.numeric(scale(w2chn)),
         w2mat_std = as.numeric(scale(w2mat)),
         w2eng_std = as.numeric(scale(w2eng)),
         w2ttl_std = as.numeric(scale(w2ttl))
         ) %>% ungroup()
```

Sample
```{r}
d_cl <- d_cl %>% 
  filter(w2a0801==1) %>% #parents who are married (and alive)
  filter(be1201==1 & be1202==1) %>% #both parents stay with children at baseline
  filter(local.resi>=7)
```

## Variables 
Dependent variables: Outcome differences between wave 2 and wave 1
```{r}
d_cl <- d_cl %>% mutate(
  chn_std = w2chn_std - w1chn_std,
  mat_std = w2mat_std - w1mat_std,
  eng_std = w2eng_std - w1eng_std,
  ttl_std = w2ttl_std - w1ttl_std,
  cog = w2cog3pl - cog3pl #Cognitive test score, standardized
) %>%
  drop_na(cog, chn_std, mat_std, eng_std, ttl_std)
```
